\documentclass[a4paper,12pt]{article}
\usepackage[latin1]{inputenc}

\title{Chapter questions on Bynum's\\ \emph{A Little History of Science}}
\author{ACN}
\date{October 2018}

\usepackage[left=2cm,top=1.5cm,hcentering,a4paper]{geometry}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1.5ex plus 0.3ex minus 0.2ex}

\begin{document}

\maketitle

\section{In the beginning} %p. 1

\section{Needles and numbers} %p. 6

\section{Atoms and the void} %p. 14

\section{The father of medicine: Hippocrates} %p. 19

\section{`The Master of Those Who Know': Aristotle} %p. 24

\section{The Emperor's Doctor: Galen} %p. 30

\section{Science in Islam} %p. 35
	
\section{Out of the Darkness} %p. 39

\section{Searching for the Philoshopher's Stone} %p. 44

\section{Uncovering the Human Body} %p. 50

\section{Where is the Centre of the Universe?} %p. 56 %priority

\section{Galileo} %p. 62 %priority

\begin{enumerate}
\item Where do some tales suggest that Galileo performed experiments dropping balls?
\item What did Galileo realize about when a ten-pound and a one-pound ball would hit the ground?
\item What did Galilio study at Pisa before he became interested in maths and physics?
\item Which religious organization did Galileo come into conflict with because of his scientific thinkings?
\item What relationship did Galileo find between the distance a ball travels rolling down a slope and the time it has been rolling?
\item Which Greek philosopher's thinking did Galileo's work update?
\item Which kind of instrument (its name means `to see far') did Galileo become interested in?
\item What did Galileo see when he looked at Jupiter?
\item Which theory of Copernicus' about how the planets move seemed to be supported by Galileo's new evidence?
\item What happened to Galileo---first in Siena and later near Florence---after his trial in 1633?
\end{enumerate}

\section{Round and Round: Harvey} %p. 68

\section{Knowledge is Power: Bacon and Descartes} %p. 74

\section{The `New Chemistry'} %p. 81

\section{What goes up\ldots: Newton} %p. 87 %priority

\begin{enumerate}
\item What language could Isaac Newton write as easily as English?
\item Which university did Isaac Newton attend in the 1660s?
\item Newton used a `method of fluxions' which he developed.  What does `flux' mean?
\item What did Newton use to break up light into colours?
\item Newton saw further than scientists had previously.  What analogy did he use to describe this?
\item Which scientific society was Newton a Fellow of (and later on, President)?
\item Name one of Newton's branches of investigation did Newton keep secret from his university.
\item Which astronomer (who has a comet named after him) visited Newton and discussed the shapes that orbiting objects make?
\item Which three famous laws were first published in the \emph{Principia}?
\item Where did Newton live for the last 30 years of his life, and what job did he do for the government?
\end{enumerate}

\section{Bright Sparks} %p. 94  %priority

\begin{enumerate}
    \item What was the kind of stone which was found to attract iron called?
    \item What happens if you rub amber very hard?
    \item In what object was electricity first able to be stored?
    \item Who linked hands and became the first group of ten people to get an electric shock?
    \item Give one thing invented by Benjamin Franklin.
    \item What did Franklin do in a lightning storm?
    \item How are buildings protected from catching fire if struck by lightning?
    \item Which unit is named after Andr\'e-Marie Amp\`ere?
    \item What common modern device did Volta play a big part in developing?
    \item What twitched when Galvani connected it to electricity?
\end{enumerate}

\section{The Clockwork Universe} %p. 100 %priority

\section{Ordering the World} %p. 107

\section{Airs and Gases} %p. 113

\section{Tiny Pieces of Matter} %p. 120

\section{Forces Fields and Magnetism} %p. 127 %priority

\section{Digging Up Dinosaurs} %p. 133

\section{The History of Our Planet} %p. 139

\section{The Greatest Show on Earth} %p. 146

\section{Little Boxes of Life} %p. 154

\section{Coughs Sneezes and Diseases} %p. 161

\section{Engines and Energy} %p. 169 %priority

\section{Tabling the Elements} %p. 175

\section{Into the Atom} %p. 182 %priority

\section{Radioactivity} %p. 189 %priority

\section{The Game-Changer: Einstein} %p. 196 %priority

\section{Moving Continents} %p. 203

\section{What Do We Inherit?} %p. 209

\section{Where Did We Come From?} %p. 217

\section{Wonder Drugs} %p. 224

\section{Building Blocks} %p. 231

\section{The Human Genome Project} %p. 237

\section{The Big Bang} %p. 243 %priority

\section{Science in Our Digital Age } %p. 251 %priority

\end{document}
