\documentclass[a4paper,11pt]{article}
\usepackage[latin1]{inputenc}

\title{Bynum}
\author{ACN}
\date{October 2018}

%\usepackage{geometry}

\begin{document}

\maketitle

\section{In the beginning}

\section{Needles and numbers}

\section{Atoms and the void}

\section{The father of medicine: Hippocrates}

\section{`The Master of Those Who Know': Aristotle}

\section{The Emperor's Doctor: Galen}

\section{Science in Islam}
	
\section{Out of the Darkness}

\section{Searching for the Philoshopher's Stone}

\section{Uncovering the Human Body}

\section{Where is the Centre of the Universe?}

\section{Galileo}

\section{Round and Round: Harvey}

\section{Knowledge is Power: Bacon and Descartes}

\section{The `New Chemistry'}

\section{What goes up\ldots: Newton}

\section{Bright Sparks}

\begin{enumerate}
    \item What was the kind of stone which was found to attract iron called?
    \item What happens if you rub amber very hard?
    \item In what object was electricity first able to be stored?
    \item Who linked hands and became the first group of ten people to get an electric shock?
    \item Give one thing invented by Benjamin Franklin.
    \item What did Franklin do in a lightning storm?
    \item How are buildings protected from catching fire if struck by lightning?
    \item Which unit is named after Andr\'e-Marie Amp\`ere?
    \item What common modern device did Volta play a big part in developing?
    \item What twitched when Galvani connected it to electricity?
\end{enumerate}

\section{The Clockwork Universe}

\section{Ordering the World}

\section{Airs and Gases}

\section{Tiny Pieces of Matter}

\section{Forces Fields and Magnetism}

\section{Digging Up Dinosaurs}

\section{The History of Our Planet}

\section{The Greatest Show on Earth}

\section{Little Boxes of Life}

\section{Coughs Sneezes and Diseases}

\section{Engines and Energy}

\section{Tabling the Elements}

\section{Into the Atom}

\section{Radioactivity}

\section{The Game-Changer: Einstein}

\section{Moving Continents}

\section{What Do We Inherit?}

\section{Where Did We Come From?}

\section{Wonder Drugs}

\section{Building Blocks}

\section{The Human Genome Project}

\section{The Big Bang}

\section{Science in Our Digital Age }

\end{document}
